---
title: DriftWatch Plotting
author: Taiki Sakai
date: 2023-08-04
output: html_document
---

## DriftWatch Custom Plot Example

This document is a short tutorial on using the existing DriftWatch functions
to create plots of specific drift tracks for reports or other uses. Start
by sourcing the functions and locating the DriftWatch database (download
this fresh from the GoogleDrive so that you have the most up-to-date GPS 
data for each drift.

```{r}
library(here)
source(here('DriftWatchFunctions.R'))
db <- here('SPOTGPS_Logger.sqlite3')
```

Then use `getDbDeployment` to pull out *all* the drift track data. Note you
can also use the `drift` argument so specify the name a specific drift or
drifts (e.g. `drift=c('ADRIFT_034', 'ADRIFT_035')`), but for this example we'll just pull
out all the data and filter down later.

```{r}
gps <- getDbDeployment(db)
str(gps)
```
 
We'll filter down to just the PASCAL drifts and plot them with `plotAPIDrift` using the 
option `simple=TRUE` and `current=FALSE`

```{r}
pascal <- filter(gps, grepl('PASCAL_', DriftName))
plotAPIDrift(pascal, simple=TRUE, current=FALSE)
```

You'll note that the plot margins are completely wonky - these will be fixed automatically
when saving a plot to a PNG file using the `filename` argument. This plot also has
shipping lanes and windcall areas as orange and purple boundaries, we can remove those
with `sl=FALSE` and `wca=FALSE`

```{r}
plotAPIDrift(pascal, simple=TRUE, current=FALSE, wca=FALSE, sl=FALSE)
```

Changing to `simple=FALSE` adds additional start/stop endpoints to the drifts, and 
tries to label them on the legend. It also adds labels of potential points of
interest on land to help orient the map, but this can get really crowded when 
trying to plot a large number of drifts.

```{r}
plotAPIDrift(pascal, simple=FALSE, current=FALSE, wca=FALSE, sl=FALSE)
```

The `plotAPIDrift` function uses R's base plotting functions, so users can also add
other bits like titles or other points to these plots using the normal base
plotting functionality.

```{r}
plotAPIDrift(pascal, simple=TRUE, current=FALSE, wca=FALSE, sl=FALSE)
title('TITLE!')
points(x=-125, y=38, col='red', cex=3, pch=17)
```
