# Downloads

Download all contents of "DriftWatch/PlottingData"
Download SPOTGPS_Logger.sqlite3, DriftWatchFunctions.R, and DriftWatch_Hourly.R from "DriftWatch"

# Folder structure
Create a "DriftWatch" folder and place all these files and folders within it
In that folder create new folders "DriftPlots" and "TestDeploymentPlots"

# Install packages

Try to source "DriftWatchFunctions.R", you will probably need to install many of the packages
listed at the top of the file

# Change to use your Google account

In "DriftWatch_Hourly.R", change line 29 from my email to your email.
You will also need to set up GoogleDrive authentication so that R
can access our Gddrive using your credentials. You can do this with

```{r}
googledrive::drive_auth(cache=TRUE)
```

# Set up task scheduler

Now you need to set this up to run every hour using the `taskscheduleR` package. If your
"DriftWatch_Hourly.R" file is something other than the current directory then you will need
to change the path accordingly. When the task scheduler is running the R script you will see
a black console window pop up on your screen (it prints out no information while running).

```{r}
install.packages('taskscheduleR')
library(taskscheduleR)
taskscheduler_create(taskname = "DriftWatch_Hourly", rscript = normalizePath('DriftWatch_Hourly.R'), 
                     schedule = "HOURLY", starttime = format(Sys.time() + 62, "%H:%M"),
                     startdate = format(Sys.Date(), '%m-%d-%Y'))
```

# Adjusting or ending the task scheduler

The easiest way to edit settings or stop the scheduled task (when you no longer want DriftWatch to
run on your computer) is by going to Windows' Task Scheduler interface. You should see a "Task Scheduler Library"
to click on, and within there our task will be named "DriftWatch_Hourly". Click on that to change any properties
or cancel it.

# Checking for issues

If plots don't seem to be uploading, you can check the "DriftWatch_Hourly.txt" log file that gets created in the
local DriftWatch folder. Scroll to the bottom of this for the most recent updates. It's hard to give 
too much advice on how to fix whatever errors might come up, but I find that the most frequent is that there are
issues with the HYCOM data download. For this you might see a cryptic error like "nc4_var_get subscript out of bounds"
or something like that. Best bet is to just delete the downloaded "HYCOMGLBycurrent.nc" file in your local DriftWatch folder,
then either wait for it to run again or you can trigger an immediate run from the Windows Task Scheduler. DriftWatch will then
download the HYCOM data again when it runs.

# Changing current data

You can change from HYCOM (current default) to HFRADAR by changing line 34 to

```{r}
useCurrent <- 3
```

# A note on run times

Typically DriftWatch will take about 10 minutes to run, depending on how much new data it has to
download and how many plots it has to upload. HOWEVER, if there have been a lot of new GPS coordinates
since the last time it was run then it may take significantly longer.